---
title             : "Analiza relației dintre inteligență și vârstă"
shorttitle        : "Inteligența și vârsta"
author: 
  - name          : "Cristian Opariuc-Dan"
    affiliation   : "1,2"
    corresponding : yes    # Define only one corresponding author
    address       : "Alea Universiății, Nr. 1"
    email         : "copariuc@gmail.com"
    role: # Contributorship roles (e.g., CRediT, https://credit.niso.org/)
      - "Equal contribution"
      - "Conceptualization"
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"
      - "Investigation"
      - "Methodology"
      - "Data curation"
      - "Formal analysis"
  - name          : "Elena Danteș"
    affiliation   : "1"
    role:
      - "Equal contribution"
      - "Writing - Review & Editing"
      - "Supervision"
      - "Project administration"
      - "Validation"
      - "Visualizaton"
      - "Data curation"
      - "Methodology"
  - name          : "Mihaela Sandu"
    afililiation   : "1"
    role:
      - "Funding acquisition"
      - "Resources"
      - "Data curation"
affiliation:
  - id            : "1"
    institution   : "Ovidius University, Constanta, Romania"
  - id            : "2"
    institution   : "Bucharest University, Bucharest, Romania"
authornote: |
  Cristian Opariuc-Dan - Faculty of Law and Administrative Sciences, Ovidius University, Constanța, Associated Professor; PhD School, Psychology and Educational Sciences, University of Bucharest, Associated Professor; PhD School, Psychology and Educational Sciences, "Al. I. Cuza" University, Iasi, Associated Professor.
  
  Elena Danteș - Faculty of Medicine, Ovidius University, PhD Professor habil.; PhD School of Medicine, Ovidius University, Constanța, PhD Professor habil.
  
  Mihaela Sandu - Faculty of Psychology and Educational Sciences, Ovidus University, Constanța, Assistant Professor
  Many thanks to Ms Georgiana Budai for their work and assistance in all research's stages, includind data collection, data quality aassurance, data screening, purification and proofreading.
  
abstract: |
  [REZUMATUL PE BAZA GHIDULUI]
  
  
  <!-- https://tinyurl.com/ybremelq -->
keywords          : "intelligence; iq; age"
wordcount         : "86 words in text body 109 words in reference section"
bibliography      : ["r-references.bib", "Proiect.bib"]
floatsintext      : no
linenumbers       : yes
draft             : yes
mask              : no
figurelist        : no
tablelist         : no
footnotelist      : no
classoption       : "man"
documentclass     : "apa7"
csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"

output            :
  pdf_document    : papaja::apa6_pdf
  word_document   : papaja::apa6_docx
  
header-includes   :
  - |
    \usepackage{ragged2e}
---

```{r setup, include = FALSE}
  library(papaja); library(foreign); library(rstatix); library(psych)
  r_refs("r-references.bib")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

# Methods
\justify
We report **how we determined our sample size, all data exclusions** (if any), all *manipulations*, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants
```{r descriptives, include = FALSE}
  source("02 - Descriptives.R")
```

The final sample comprised `r desc[1,2]` Romanian participants, aged `r desc$min[1]` to `r desc$max[1]` years (M=`r desc$mean[1]`, SD=`r desc[1,4]`), `r as.numeric(gen.p[2])`% female. The intelligence quotient was ranged between `r desc$min[2]` and `r desc$max[2]` (M=`r desc$mean[2]`, SD=`r desc$sd[2]`)



## Material

## Procedure

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.


# Results

# Discussion


\newpage

# References

::: {#refs custom-style="Bibliography"}
:::
